# Sensitivity spline plots {#sens_splines}

---
output:
  pdf_document:
    keep_tex: yes
fontfamily: mathpazo
fontsize: 9pt
---

\raggedright


```{r setup_splines, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
# source(paste0(here::here(), "/0-config.R"))
```

### Primary spline figures  - meta-analysis of cohort specific splines

```{r, echo = FALSE}


include_graphics(paste0(here::here(), "/ki-longitudinal-manuscripts/figures/risk-factor/spline_grid.png"))

```

### Spline figures - meta-analysis of cohort specific splines, different parameters

Centered at age = 1 says and with 6 degrees of freedom 

```{r, echo = FALSE}

include_graphics(paste0(here::here(), "/ki-longitudinal-manuscripts/figures/risk-factor/spline_grid_sens.png"))

```

### Primary spline figures - Single spline fit to all the data

```{r, echo = FALSE}

include_graphics(paste0(here::here(), "/ki-longitudinal-manuscripts/figures/risk-factor/spline_grid_sens2.png"))
```

### Primary spline figures - splines fit through meta-analyses of monthly means of Z-scores 

```{r, echo = FALSE}

include_graphics(paste0(here::here(), "/ki-longitudinal-manuscripts/figures/risk-factor/spline_grid_sens3.png"))


```
